R Notebook

### 2020-02-09 Rcodes/JAGS_practice.Rmd
jags lagged: errors to be questioned

---
title: "R Notebook"
output: html_notebook
---
# Following an online tutorial

@@

```{r}
install.packages('runjags')
library(runjags)
modelString = "
model{
for (i in 1:N) {
y[i] ~ dnorm(mu, phi)
} 
mu ~ dnorm(mu_0, phi_0)
phi ~ dgamma(alpha, beta)
}
"

@@

```{r}
y <- CEdata$LogTotalExpLastQ
N <- length(y)
the_data <- list(
  'y'=y,
  'N'=N,
  'mu_0'=5,
  'phi_0'=1/1^2,
  'alpha'=1,
  'beta'=1
)

@@

>>>>

---
title: "R Notebook"
output: html_notebook
---
# Following an online tutorial (no data...)

@@

summary: 
in the model, as a string, we put the likelihood and the parameters of interest with their prior distribution.
```{r}
install.packages('runjags')
install.packages('coda')
```

```{r}
library(runjags)
modelString = "
model{
for (i in 1:N) {
y[i] ~ dnorm(mu, phi)
} 
mu ~ dnorm(mu_0, phi_0)
phi ~ dgamma(alpha, beta)
}
"

@@

From here, the list named as the_data, we plug in the values of the parameters for the prior including the number of observation for likelihood (N).

Posterior result is obtained by run.jags function where we plug in our data (the_data) which we set the values of the parameters for prior, we state our interest parameters as monitor. I assume modelString goes into the first argument here.
```{r}
y <- CEdata$LogTotalExpLastQ
N <- length(y)
the_data <- list(
  'y'=y,
  'N'=N,
  'mu_0'=5,
  'phi_0'=1/1^2,
  'alpha'=1,
  'beta'=1) # this we where the pre-set priors given to the model
  posterior <- run.jags(
    'norm_model.jags',
    data = the_data,
    monitor = c('mu','phi'),
    n.chains=1,
    adapt=1000,
    burnin=2000,
    sample=5000,
    thin=1
  )

summary(posterior)

@@

# Another JAGS Tutorial 
[from here](https://rstudio-pubs-static.s3.amazonaws.com/272658_ae4d482c86514674be17042c852ebbfc.html)

```{r}
setwd("../../meta-analysis-Bayesian/")
data =read.csv('data1.csv')
head(data)
```

```{r Defining values}
library(coda)
N <- length(data$y)

data <- list('N'=N, 
             'y'=data$y,
             'V'=data$V)

inits <- list(d=0.0)

```{r Enter the Model}
cat("model{
for (i in 1:N) {
P[i] <- 1/V[i]
y[i]~dnorm(d,P[i])
}
# Define the priors
d ~ dnorm(0,0.00001)

# Transfomr the ln(OR) to OR
OR <- exp(d)
}

    ", file='model_test.txt')
```

```{r}
library(rjags)
jags.m <- jags.model(file='model_test.txt',data=data, inits=inits, n.chains = 1, n.adapt = 500,)
```
```{r}
params <- c('d','OR')
samples <- coda.samples(jags.m, params, n.iter=10000)
```

```{r}
summary(samples)
```

```{r}
summary(window(samples, start=5001))
```

```{r}
plot(samples)
```

_______________________________________________________________
